A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-15 manuscript/reply_to_reviewers.tex

		\begin{refquote}
		1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realise that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for stressing the need to further acknowledge previous work in the field. As this was also emphasised by other reviewers, we have taken this carefully \emph{ad notam} and expanded our references to earlier work as much as possible given length restrictions. We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors. We hope that the introduction now presents a more thorough sample of previous work.

		\begin{refquote}
		Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realisation – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
		\end{refquote}

@@

			\textbf{R:} We agree, and have added a citation to Bartomeus as requested. In terms of why we will have omitted references to other similar papers and to some less conceptual and empirical attempts, we must stress that we are not striving for a comprehensive review but rather trying to reach a particular audience with a particular message, for which we find MEE the ideal forum. The length and formatting constraints of an MEE article mean that, for the sake of brevity and clarity, we cannot cite all previous work concerning detection probability.

		\begin{refquote}
			Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
		\end{refquote}

		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices. As said, we have done our best to improve our coverage of previous work, within the limits offered by the current format.

		\begin{refquote}
		Line 89.  In Weinstein and Graham (Ecology Letters) the processes modelled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
		\end{refquote}

		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all. Instead, we discuss repeated sampling in a section dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certainly not). We hope that this is less confusing.

@@

		\textbf{R:} We believe that the Reviewer has  misunderstood the point of our comments on sampling effort. Several of their comments suggest that we are advocating for reducing sampling effort. This is emphatically not the case. Rather, we assumed that field researchers already sample to the maximum extent possible given their time and resource constraints and so a call to "sample more" would not be helpful. We now address this assumption explicitly in an appendix (Appendix S2)  dedicated to the potential for sampling effort to reduce uncertainty about interactions. Below, we address the Reviewer's sampling-related comments one by one.

		\begin{refquote}
		Line 94.  I find this a very odd argument against sampling multiple times.  So, if you sample more you might see more then understand the system less?  The logic does not make sense to me. 
		\end{refquote}

		\textbf{R:} Of course sampling more does not lead to less understanding. It can, however, reveal knowledge gaps (as when a rare species is detected, revealing our ignorance of its interactions). This is not an argument against multiple sampling but a statement that increased sampling is likely to lead to the addition of more "false zeros" as species about which we know little are added to the network.

		\begin{refquote}
		Line 107.  There is a lot of literature in wildlife ecology emphasising the importance of repeat sampling for estimating detection probability.  Is this just wrong?  If so this does need more explanation in the context of this literature.
		\end{refquote}

@@

			\end{quotation}

	7. Why not always model probabilities of co-occurrence? [[done]]

		\begin{refquote}
		Line 142.  But shouldn’t you model the probability of two species co-occurring?  The authors have a paper doing this…. Is that not a good idea?
		\end{refquote}

		\textbf{R:} Modelling the probability of co-occurrence is an option for many systems (e.g., aquatic food webs where ranges of fish species are fairly well-known, as in~\citet{Gravel2013}). In some systems, however, the factors affecting probabilities of co-occurrence may not be known. We therefore cannot suggest modelling co-occurrence as a panacea. Instead, we now emphasise that co-occurrence probabilities are one thing that could be included in a prior (lines XX-XX - section Informative priors). 
		\smallskip
		The fact remains that a lack of observed interactions between species which do not co-occur tells us nothing about whether these species \emph{could} interact if they should begin to co-occur (e.g., following a range shift). Following the Reviewer's suggestion, we have revised our manuscript to clarify our technology. In particular, we have taken care to specify which level of uncertainty we are addressing at different points in the manuscript. We hope that this will remove some of the confusion about whether or not modelling different components of uncertainty/sampling more is a good idea.

@@

	8. Issue of testing hypotheses based on inputs into models [[done]]

		\begin{refquote}
		Line 121.  I think one of the reason non-Bayesians’ are not comfortable with the approach is that if you put in prior information on something like trait matching and test for trait matching and then discover trait matching is important – what does it mean?  Maybe this is too obvious (I realise there are tons of papers on how to choose priors) but I wonder if it is worth explaining (would a box or something be worthwhile?  I leave it up to the authors/editor)?  Maybe the issue could be acknowledged and an appropriate paper cited?
		\end{refquote}

@@

		\textbf{R:} The redundant line has been removed. Thank you for pointing this out.

	10. Unsure about the point of filtering networks [[done]]

		\begin{refquote}
		Line 295 to 302.  I would think that this second step (i.e., filtered networks) is to explore sampling not to determine how networks will be influenced by uncertainty?  Do you need the filtering step to evaluate uncertainty (as written it seems that this is the case)?
		\end{refquote}

		\textbf{R:} The filtering was intended to show how uncertainty likely warps our current understanding of network properties like connectance. If we do not observe 20-50\% of the interactions in a network, then many network properties in the published literature will be inaccurate. Even worse, networks compiled under different levels of uncertainty (e.g., species with more or less variable traits, or studies with multiple sampling methods or only one) or with different sampling efforts will have network structure metrics that are inaccurate to different degrees. Filtering networks in the way that we do could give an idea of how many networks are missing, but we do not think it is necessary to evaluate uncertainty (we believe that examining the posterior distributions directly is a better approach there). We have rephrased these lines (XX-XX) to emphasise that the filtered networks are intended to demonstrate the consequences of uncertainty more than anything else.

@@

		\begin{quotation}
			Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. 
		\end{quotation}

	11. Scepticism about sampling requirements to be sure interactions do not occur [[done]]

		\begin{refquote}
		Line 361.  I find the statement that 30-50 individuals need to be evaluated a bit strong.  This statement is based on this study – are all systems like the gall system?  If species are specialised or bound to interact for some other reason (i.e., co-occurring when there are few other resources) wouldn’t you need to observe fewer individuals?  The point of the method is that you can estimate how many individuals are needed…. This is great!  But given that this can be estimated from any given system why give a value from one system and state that is what is required?  It defeats the point of the very nice method proposed…??
		\end{refquote}

@@

		\textbf{R:} The point of our method is not actually to quantify the amount of sampling needed. Although the ideal sampling effort \emph{can} be calculated using the framework we put forward (as we demonstrate), the real point is to quantify how uncertain we are that an interaction we do not observe really does not occur. Given this, we do not think that recommending uncertainty be explicitly stated undermines our point.

		The Reviewer's suggestion that we might need fewer samples for species that are "specialised or bound to interact for some other reason" reflects a very strong prior. In this case, yes we would need fewer samples for the species concerned. With sufficiently strong priors, it is not necessary to sample at all! For example, in most food webs it is assumed that basal resources will never consume prey even if a given resource and a given animal are never observed co-occurring and it is generally accepted that there is very low uncertainty about these zeros. In many cases, the assumptions involved in excluding interactions are less clear-cut and different researchers may disagree about which species are "bound to interact" (or not to interact). The concept of pollination syndromes is one example - many flower visitors are less rigidly specialised on particular flower types than initially thought~\citep{Ollerton2009}. To address such "forbidden links", we now suggest that researchers explicitly state both the uncertainty about data-based zeros and the assumptions by which they create structural zeros. This will allow future researchers to evaluate the uncertainty about all interactions in a network as the state of expert knowledge changes. We hope that this expanded recommendation (lines XX-XX) is clearer.

@@

	5. Description of causes of uncertainty poorly integrated with the case study [[done]]

		\begin{refquote}
		L50 This is a nice and clearly explained description of the problem that many network ecologists ignore, or are unaware of.
		Section from L50. This section is valuable, but had very weak links with the empirical analysis later in the paper. For instance in the example of the gall-formers, there was not formal discussion about the different sources of uncertainty. 
		\end{refquote}

		\textbf{R:} As we state in the section \textbf{Estimating uncertainty}, we usually cannot distinguish different sources of uncertainty in empirical data. Those studies which attempt to do so (e.g.,~\citet{Graham2018}) remove process uncertainty by assuming constant interaction probabilities during a short, intense sampling period and also assume that we know the true set of feasible interactions. This may be the case for Graham and Weinstein's relatively small and well-studied system but is not likely to be true for systems containing hundreds of species, systems containing recently-arrived species, systems just beginning to be studied, etc.

		To make this clearer, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is actually unfeasible). We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.

@@

		\begin{refquote}
		L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
		\end{refquote}

		\textbf{R:} Long-term interactions may be easier to detect, but this does not necessarily translate into reduced process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section. Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).

			\begin{quotation}

				Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2015}. If these infected individuals do not happen to be included in a sample, their interactions will be missed.

@@

		\textbf{R:} Due to space constraints, we have refrained from adding an extensive description of Jensen's inequality here, but are confident that readers can find a fuller description in the online literature if they choose.

	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[done]]

		\begin{refquote}
		L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics. I’m not sure of the solution and would welcome thoughts on this in the paper.
		\end{refquote}

		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occur at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study. We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S2}. Note that each posterior web is a prediction of the true metaweb and not a local realisation of some interactions drawn from the feasible set. These local webs are more akin to our "filtered webs" in which observed interactions are not guaranteed to appear. We have also added a line (lines XX-XX) to make this clear.
